Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
verbal nouns
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60955 72bbbca6-d526-0410-a7d9-f06f51895060

@@

>>>>

Verbal adverb clauses in Kazakh act as a clausal verbal adjunct, essentially allowing a whole verb phrase to act as an adverb.  The dependency relation between the verbal adverb and the head verb is \udtag{advcl}, per UD documentation.  An example is provided in figure~\ref{fig:gna}.

@@

Verbal nouns allow a whole verb phrase to be used as a nominal, and the resulting verbal noun phrase may be used as a subject or object of a verb.  When used as the subject of a verb, verbal noun phrases receive the UD label \udtag{subj} and when the object of a verb \udtag{ccomp}.  An example of a verbal noun phrase used as a \udtag{ccomp} dependency of the main verb is given in table~\ref{fig:gerdat}.
